Yeast RNA-seq 48 sample simulation study: Unimodal alternative, 500 DE genes

### 2018-09-18 datasets/RNA-Seq/yeast-simulation-bimodalalternative-highpi0.Rmd
Add plot of logistic informative covariate

First, here's a function that will generate sampling weights for test statistics
of DE genes that downweights observations near zero, as well as extremely large values.

>>>>

First we'll illustrate the logistic curve used to simulate the informative covariate. 
In this study we'll sample from a logistic curve and use these values as probability 
weights when  selecting DE genes. A weakly informative covariate will be generated by 
adding noise to the strongly informative covariate.

```{r}
x <- seq(0,10, by = 0.1)
infcov <- 1 / (1+exp(-x + 5))
plot(x, infcov, type = "l", ylab = "informative covariate")

plot(infcov,  pmin(1, abs(infcov + rnorm(length(x), 0, 0.25))), 
     ylab = "weak covariate", xlab = "true covariate")
```

Next, here's a function that will generate sampling weights for test statistics
of DE genes that downweights observations near zero, as well as extremely large values.

### 2018-09-18 datasets/RNA-Seq/yeast-simulation-highpi0.Rmd
Add plot of logistic informative covariate

>>>>

First we'll illustrate the logistic curve used to simulate the informative covariate. 
In this study we'll sample from a logistic curve and use these values as probability 
weights when  selecting DE genes. A weakly informative covariate will be generated by 
adding noise to the strongly informative covariate.

```{r}
x <- seq(0,10, by = 0.1)
infcov <- 1 / (1+exp(-x + 5))
plot(x, infcov, type = "l", ylab = "informative covariate")

plot(infcov,  pmin(1, abs(infcov + rnorm(length(x), 0, 0.25))), 
     ylab = "weak covariate", xlab = "true covariate")
```
